% CSC258 Final Project Report
% Author: Haoyan Wang

\documentclass[12pt, draft]{report}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=2.5cm]{geometry}
\usepackage{parskip}
\usepackage{enumitem}

% Document metadata
\title{Tower of Babel}
\author{Haoyan Wang, Poru Tseng}
\date{Dec 1, 2019}

% Document starts here
\begin{document}
\maketitle
\newlist{caselist}{itemize}{1}
\setlist[caselist]{
  label=\textsl{Case},
  labelindent=0pt, %customize value for distance from left margin to "Case"
  leftmargin=4em, %customize value for distance from left margin to item content
  labelsep=*,
  align=left
}

\section*{Introduction}
Our game, Tower of Babel, is designed upon the idea that in ancient greek tale,
people once tried to build a tower to reach the realm of god. The game let the 
player be the builder of the tower. By stacking building blocks (boxes) from the
bottom to the top, the player can decide where and when to place the box, and the 
building boxes form a tower. 

\subsection*{Game Demo}
Thegame is configurated in the way that the boxes will constantly moving 
horizontally from the one side of the screen to the opposite side, and the next 
box will not stay on top if it does not overlap on the previous box. There will 
also be chances given to the player, and it costs one chances to build one level 
of the tower while the goal is to reach as high as the tower canget to.

When the game ends, you are shown the game-end dialog, which reports the 
height of your tower and additionally, it gives you the option to restart the game. 

\subsection*{Why this project}
First of all, this game is fun due to the infinite property of this game. The higher
the tower, the harder to build it higher and it spurs you to take the challenges.

Secondly, the game is fun to work on.

\pagebreak
\section*{Implementation}
\subsection*{Game Datapath}
\subsection*{Game Finite State Machine}
\subsection*{I/O and Peripherals}

\pagebreak
\section*{Results}
\subparagraph*{How did it go}

\pagebreak
\section*{Discussion}
\subsection*{Playability}
\subsection*{What We Learned}
\subsection*{What could be improved}
% use a page break to start a new page and ends this section
\pagebreak
\section*{Conclusion}

\pagebreak
\section*{Appendix}


\pagebreak
\section*{formulaDemo}
\begin{enumerate}
    \item[(a)]
        \begin{itemize}
            \item[] $n > c$ and $n > k$
        \end{itemize}
        \begin{align*}
            n^n = n \cdot n^{n-1} &> c\cdot n^{n-1}\\
            &\geq c\cdot n^k
        \end{align*}
\end{enumerate}
\end{document}